% ===================================================
\chapter{Background}
% ===================================================


% ===================================================
\section{Notation for Traditional Path Planning}
% ===================================================

[TODO avoid definition notation]
\theoremstyle{definition}
\begin{definition}{Maximal Reachable Set}
A fibration is a mapping between two topological spaces that has the homotopy lifting property for every space $X$.
\end{definition}

Taken from page 17 of \cite{lavalle2006planning}:

\begin{definition}{State}
Temp
\end{definition}

\begin{definition}{state space $X$}
Finite or countably infinite set of states.
\end{definition}

\begin{definition}{Initial State $x_1 \in X$}
Temp
\end{definition}

\begin{definition}{Goal Set $X_G \subset X$}
Temp
\end{definition}

\begin{definition}{Time}
Temp
\end{definition}

\begin{definition}{Action $u$}
Temp
\end{definition}

\begin{definition}{action space $U(x)$}
A finite set of actions for each state $x \in X$
\end{definition}

\begin{definition}{(state transition function)}
 $f(x,u) \in X$
A finite set of actions for each state $x \in X$
\end{definition}

\begin{definition}{Feasibility Criterion}
Temp
\end{definition}

\begin{definition}{Optimality Criterion}
Temp
\end{definition}

\begin{definition}{Plan}
Temp
\end{definition}

\begin{definition}{Potential Function}
Temp
\end{definition}

\begin{definition}{Configuration Space}
Temp
\end{definition}

\begin{definition}{XYZ Space}
Temp
\end{definition}

\begin{definition}{XY Space $M$}
Temp
\end{definition}

% ===================================================
\chapter{Related Work}
% ===================================================
% show my problem is unsolved
% • show my problem is interesting
% • show my idea works
% • show how my idea compares to other ideas
% • No related work yet! Include at end.
% – Problem 1: describing alternative approaches gets between the reader
% and your idea (I feel tired)
% – Problem 2: the reader knows nothing about the problem yet; so your
% (carefully trimmed) description of various technical tradeoffs is abso-
% lutely incomprehensible (I feel stupid)
% – instead, Concentrate single-mindedly on a narrative that
% ∗ Describes the problem, and why it is interesting
% ∗ Describes your idea
% ∗ Defends your idea, showing how it solves the problem, and filling
% out the details
% ∗ On the way, cite relevant work in passing, but defer discussion to
% the end
% • show how my idea compares to other ideas
% • Be generous to the competition. In his inspiring paper [Foo98] Foogle shows....
% We develop his foundation in the following ways...
% • Giving credit to others does not diminish the credit you get from your paper
% • Acknowledge weaknesses in your approach
% • Failing to give credit to others can kill your paper: You don’t know that it’s
% an old idea (bad) or You do know, but are pretending it’s yours (very bad)

% ====================
\section{Parking Lot Detection}
% ====================
% Wang \cite{wang2014automatic}
% Jung \cite{jung2014semiautomatic}
% 
% Pouria's thesis \cite{talebifard2014risk}
% Talk: \url{https://www.youtube.com/watch?v=Db7EhLYf-Yk#t=1h11m07s}
% 
% 
% file:papers/jiang1999sensor.pdf
% Basic old paper on parallel parking. Uses ultrasonic sensor, then
% fixed planning.
% 
% file:papers/fairus2011development.pdf
% Old paper. Scanning methods.
% 
% file:papers/wang2013automatic.pdf
% Newish lit review of automatic parking
% 
% file:papers/abad2007parking.pdf
% Parking space detection using 3d vision. Parallel parking
% 
% file:papers/lalonde2012single.pdf
% CVPR workshop paper.
% 
% file:papers/suhr2010automatic.pdf
% Good! Solving my problem, but with a laser rangefinder.
% found from: http://www.mathworks.com/matlabcentral/answers/126413-how-to-detect-free-spots-in-a-parking-area
% 
% file:assets/WheelchairGuide.pdf

% ====================
\section{SLAM}
% ====================

LSD-Slam and PTAM for monocular seem to be state-of-art: \url{http://vision.in.tum.de/research/lsdslam}

review paper: \url{http://www-personal.acfr.usyd.edu.au/tbailey/papers/slamtute2.pdf}

2009 review paper: \url{http://www.le2i.cnrs.fr/IMG/publications/2172_Muhammad_EI_2009.pdf}

% ====================
\section{Collision Avoidance}
% ====================
Old paper using quadtrees\cite{ghoshray1996comprehensive}

Bigdog \cite{raibert2008bigdog}

Springer handbook of robotics \cite{siciliano2008springer}: Vector field histograms, as described in Pouria's thesis \cite{talebifard2014risk}


% ====================
\section{Time Optimal Trajectory Planning}
% ====================
\cite{fiorini1996time}

\section{Hardware}

[TODO photo]

We choose and fix the hardware used beforehand.

We use an RGB-D sensor due to its suitability to the problem:
it works well indoors, where the target users will be using the wheelchairs; it
is cost effective; it provides depth information with adequate accuracy.

We use only one camera. This is for simplicity. Each camera saturates its USB
controller, hence a computer must have as many USB controllers as cameras.
An additional calibration step to register the information, increasing the
computational costs even further than the linear factor. 
One can argue a limitation of using one RGB-D sensor is the depth measurements
have a range of around 0.6 m to 8 m, with a field of view of 43 degrees
vertically by 57 degrees horizontally (TODO better reference) \cite{endres2014catadioptric},
comparatively limited to lidars with fields of view of 180 degrees. Some work
\cite{endres2014catadioptric} has been done using two mirrors to split the field
of view of a single camera to cover both the front and rear view. Our work
sticks to a single camera for simplicity, though it can be naturally extended.

We mount the RGB-D camera downwards. However, we do not rely on a specific angle
to keep the solutions generalizable to systems that might have different camera
angles. The only assumption is the ground plane is visible.

We use an Asus RGB-D camera as it is smaller and less obtrusive than the Kinect
and does not require an additional power plug; it gets its power entirely from
USB.


We use a (TODO model) by (TODO) 

We use a Lenovo W530 laptop with 
\begin{itemize}
\item Intel Core i7-3720QM Processor
\item 8GB RAM
\item 120GB SSD
\item NVIDIA Quadro K1000M Graphical Processing Unit
\item Two dedicated USB controllers for USB 2.0 and USB 3.0
\item Ubuntu 14.04 64-bit
\item Robotic Operating System (Indigo release)
\end{itemize}

% ======================
\endinput
Any text after an \endinput is ignored.
% ======================
% ===================================================
\section{Robotics Pipelines}
% ===================================================

% ---------------------------------------------------
\subsection{Robotic Operating System}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Robotic Operating System}
% ---------------------------------------------------

% ===================================================
\section{Modeling}
% ===================================================

% ---------------------------------------------------
\subsection{Classification}
% ---------------------------------------------------
Modeling 

% ---------------------------------------------------
\subsection{Bayesian Stuff}
% ---------------------------------------------------
Chiu-Liu Trees

% ---------------------------------------------------
\subsection{Markov Chains, MDPs, POMDPs}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Reinforcement Learning}
% ---------------------------------------------------
Value function, reward function

% ---------------------------------------------------
\subsection{Path Planning}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Bandit Problems}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Feasibility}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Game Theory}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Control}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Rotations}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Distance Transforms and Geodesics}
% ---------------------------------------------------

% ---------------------------------------------------
\subsection{Visual Servoing}
% ---------------------------------------------------
% https://en.wikipedia.org/wiki/Visual_servoing
